Manuscript Figures

### 2024-05-29 Manuscript_Figures.Rmd
Create stacked bar chart of biomass

@@

mapcodes %>%
  ggplot() +
  geom_hline(yintercept = 600, linetype = "dashed") +
  geom_vline(xintercept = 200, linetype = "dashed") +
  geom_point(aes(X,Y,color=SPECIES_SYMBOL,size=DBH), shape=16) +
  scale_color_colorblind() +
  coord_equal() +
  labs(X = "X (m)",
       Y = "Y (m)",
       color = "Species") +
  theme_bw()
#TODO: Replace species codes with species names
```

>>>>

### Stacked bar chart of species composition in burn plot
```{r}
bp_mapcodes <- unique(as.vector(values(crop(IC_map, bp4))))
BA_plot <- before_after %>% 
  filter(MapCode %in% bp_mapcodes) %>%
  group_by(pre_post, SpeciesName) %>%
  summarize(CohortAge_Avg = mean(CohortAge),
            CohortBiomass_Sum = sum(CohortBiomass)) %>%
  mutate(pre_post = factor(pre_post, levels = c("Initial Conditions",
                                                "Fire2-Dry",
                                                "Fire2-Wet",
                                                "Fire5-Dry",
                                                "Fire5-Wet"))) %>%
  mutate(SpeciesName = case_when(SpeciesName=="LobPine" ~ "Loblolly Pine",
                                 SpeciesName=="LongleafPine" ~ "Longleaf Pine",
                                 SpeciesName=="SlashPine" ~ "Slash Pine",
                                 SpeciesName=="TulipTree" ~ "Tulip Poplar",
                                 SpeciesName=="RedMaple" ~ "Red Maple",
                                 SpeciesName=="SweetGum" ~ "Sweetgum",
                                 SpeciesName=="WhiteOak" ~ "White Oak",
                                 SpeciesName=="TurkeyOak" ~ "Turkey Oak",
                                 SpeciesName=="ShortPine" ~ "Shortleaf Pine")) %>%
  mutate(SpeciesName = factor(SpeciesName,
                              levels = c(
                                "White Oak",
                                "Turkey Oak",
                                "Red Maple",
                                "Sweetgum",
                                "Tulip Poplar",
                                "Shortleaf Pine",
                                "Slash Pine",
                                "Loblolly Pine",
                                "Longleaf Pine"
                              )))

stacked_barchart <- BA_plot %>%
  ggplot() +
  geom_bar(stat="identity",aes(pre_post,CohortBiomass_Sum, fill=SpeciesName)) +
  scale_fill_colorblind() +
  labs(x="LANDIS Run",
       y="Total Biomass (kg)",
       fill="Species") +
  theme_bw()
stacked_barchart

ggsave("biomass_barchart.jpg",path = here("Plots"), height=4)
```

@@

mapcodes_vect <- vect(mapcodes, geom=c("X", "Y"), crs="", keepgeom=FALSE)

tree_polys <- list()
for(i in 1:nrow(mapcodes_vect)){
  tree_i <- mapcodes_vect[i,]
  buffer_i <- buffer(tree_i, width = mapcodes_vect$CD_m[i]/2)
  tree_polys[[i]] <- buffer_i
}
mapcodes_poly <- vect(tree_polys)
writeVector(mapcodes_poly, here("Plots","sample_mapcode_canopies.shp"))
mapcodes_poly <- mapcodes_poly %>%
  arrange(CD_m) %>%
  mutate(SpeciesName = case_when(SPECIES_SYMBOL=="PITA" ~ "Loblolly Pine",
                                 SPECIES_SYMBOL=="PIPA2" ~ "Longleaf Pine",
                                 SPECIES_SYMBOL=="PIEL" ~ "Slash Pine",
                                 SPECIES_SYMBOL=="LIST2" ~ "Tulip Poplar",
                                 SPECIES_SYMBOL=="ACRU" ~ "Red Maple",
                                 TRUE ~ "Other")) %>%
  mutate(SpeciesName = factor(SpeciesName,
                              levels = c(
                                "Other",
                                "Red Maple",
                                "Tulip Poplar",
                                "Slash Pine",
                                "Loblolly Pine",
                                "Longleaf Pine"
                              )))

new_colors <- colorblind_pal()(8)[c(1,2,4,5,6)]
example_mapcode <- ggplot() +
  geom_hline(yintercept = 600, linetype = "dashed") +
  geom_vline(xintercept = 200, linetype = "dashed") +
  geom_spatvector(data=mapcodes_poly, aes(fill=SpeciesName, color=SpeciesName), alpha=0.7) +
  scale_fill_manual(values = new_colors) +
  scale_color_manual(values = new_colors) +
  labs(x = "X (m)",
       y = "Y (m)",
       fill = "Species",
       color="Species") +
  theme_bw()
example_mapcode
ggsave("example_mapcode.jpg",path = here("Plots"))

#TODO: Replace species codes with species names
```
